Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses

### 2014-11-20 doc/LinksToDAG_final.tex
Expanded the caption of figure 2

\begin{figure}[t!]
  \small
  \centering
  \includegraphics[width=0.7\textwidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Convergence to the direction mapping obtained on the largest run.  Precision relative to that run is very high even for small datasets.  Recall grows as more link types are seen.}\label{fig:convergence}
  \vspace{-6pt}
\end{figure}

>>>>

\begin{figure}[t!]
  \small
  \centering
  \includegraphics[width=0.7\textwidth, keepaspectratio=true]{figure/precision_recall.png}
  \caption{Convergence to the direction mapping obtained on the largest run.  Precision of the directional assignments in smaller runs relative to the largest run is high even for small datasets.  Recall grows as more link types are seen and directionalized.}\label{fig:convergence}
  \vspace{-6pt}
\end{figure}
